---
title: "15456141_appendix1"
author: "Rifayat Uddin"
date: "1/25/2019"
output: pdf_document
---

For this paper's data analysis, I chose to use the Agresti-Coull confidence intervals for all the 40 commuting zone given in the sample. This is shown in Part 1. Part 2 shows the calculations for the upward mobinility proportions for the regions. Part 2 also has the necessary calculations and comparisons to see if they're the same. 

```{r}

data = read.csv("http://dept.stat.lsa.umich.edu/~bbh/s485/data/mobility1.csv")
```


Part 1

Agresti-Coull Confidence interval 
In this part, we're finding the confidence intervals for all the 40 commuting zones that we're going to be looking at. 

```{r}
interval = function(n, p_hat, k) {
  x = p_hat*n
  x_tilda = x + k^2/2 
  n_tilda = n + k^2

  p_tilda = x_tilda/n_tilda
  q_tilda = 1 - p_tilda
  
  p_tilda = x_tilda/n_tilda
  vec = c(p_tilda-k*sqrt(p_tilda*q_tilda)*n_tilda^(-0.5),
  p_tilda+k*sqrt(p_tilda*q_tilda)*n_tilda^(-0.5))
  return(vec)
}

confidence_interval = matrix(nrow=40, ncol=2)
for (i in 1:40) {
  if (interval(data[i,6], data[i,7], 1.96)[1] < 0) {
    confidence_interval[i,1] = 0 } 
  else {
    confidence_interval[i,1] = signif(interval(data[i,6], data[i,7], 1.96)[1], digits=3) 
  }
  confidence_interval[i,2] = signif(interval(data[i,6], data[i,7], 1.96)[2], digits=3)
}


confidence_interval = as.data.frame(confidence_interval) # Change names of conf_int 
colnames(confidence_interval)[2] = "Lower_Bound"
colnames(confidence_interval)[1] = "Upper_Bound" 

confidence_interval

data = append(data, confidence_interval) 
data = as.data.frame(data)

library(ggplot2)
west_plot = ggplot(data[data[,3] == 'west',], aes(x = zone, y = p.upmover)) + geom_point(size=4) + ggtitle("Confidence Interval of Upward Mobility in the West") + geom_errorbar(aes(ymax = Upper_Bound, ymin = Lower_Bound)) + scale_x_discrete(name="Zone") + scale_y_continuous(name="Upward Mobility")

south_plot = ggplot(data[data[,3] == 'south',], aes(x = zone, y = p.upmover)) + geom_point(size=4) + ggtitle("Confidence Interval of Upward Mobility in the South") + geom_errorbar(aes(ymax = Upper_Bound, ymin = Lower_Bound))  + 
  scale_x_discrete(name="Zone") + scale_y_continuous(name="Upward Mobility") 

midwest_plot = ggplot(data[data[,3] == 'midwest',], aes(x = zone, y = p.upmover)) + geom_point(size=4) + ggtitle("Confidence Interval of Upward Mobility in the Midwest") + geom_errorbar(aes(ymax = Upper_Bound, ymin = Lower_Bound)) +  scale_x_discrete(name="Zone") + scale_y_continuous(name="Upward Mobility") 

northeast_plot = ggplot(data[data[,3] == 'northeast',], aes(x = zone, y = p.upmover)) + ggtitle("Confidence Interval of Upward Mobility in the Northeast") + geom_point(size=4) + geom_errorbar(aes(ymax = Upper_Bound, ymin = Lower_Bound)) + scale_x_discrete(name="Zone") + scale_y_continuous(name="Upward Mobility")

west_plot
south_plot
midwest_plot
northeast_plot


```

Part 2)

Part b)
```{r}




#Likelihood Testing Work:




west = data[data$region=="west",]
west

midwest = data[data$region=="midwest",]
midwest

northeast = data[data$region=="northeast",]
northeast

south = data[data$region=="south",]
south



boxplot(midwest$p.upmover, west$p.upmover, south$p.upmover, northeast$p.upmover, names=c("Midwest","West","South", "Northeast"))

title("Upward Mobility Probability")



# vector for regions
vector_regions_n = c(sum(west$n.lowstart),
        sum(midwest$n.lowstart),
        sum(northeast$n.lowstart),
        sum(south$n.lowstart))
vector_regions_n


# A Vector for the Regions Proportions 

proportions_region = c(sum(west$n.lowstart * west$p.upmover)/sum(west$n.lowstart),sum(midwest$n.lowstart * midwest$p.upmover)/sum(midwest$n.lowstart), sum(northeast$n.lowstart * northeast$p.upmover)/sum(northeast$n.lowstart), sum(south$n.lowstart * south$p.upmover)/sum(south$n.lowstart))

proportions_region

# Likelihood function
likelihood_func = function(p) {
  value = sum (dbinom(vector_regions_n*proportions_region, size=vector_regions_n, prob=p, log=T)) 
  return(value)
}

# Likelihood test
2*(likelihood_func(proportions_region) - likelihood_func( sum(vector_regions_n*proportions_region)/sum(vector_regions_n)))


# p-value to compare 
pchisq(2*(likelihood_func(proportions_region) - likelihood_func( sum(vector_regions_n*proportions_region)/sum(vector_regions_n))), 3, lower=F)


```
